IRS-Aided SWIPT:\\Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-08-12 assets/waveform_wit_modulated.tex
:bento: Update assets

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,3.296in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=5,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213595499958\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

@@

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,2.586in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=3.16339693422903,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	3.16197544010622\\
2	3.16257985135002\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	3.16115798980538\\
2	3.16339693422903\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,1.877in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=2.24021589430493,
ytick={0, 2, 4},
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	2.23378952118842\\
2	2.23654464483002\\
3	2.23679993610816\\
4	2.23713622127432\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.22545319620151\\
2	2.23919103086275\\
3	2.23937811584463\\
4	2.24021589430493\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,1.168in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=2,
ytick={0, 1, 2},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.57492536161738\\
2	1.58019558798915\\
3	1.58142030797172\\
4	1.58199169722726\\
5	1.58244513043393\\
6	1.58255247448636\\
7	1.58277901011216\\
8	1.58278544606781\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.54658301793324\\
2	1.57890604600973\\
3	1.58567053153604\\
4	1.58602764687811\\
5	1.58742152113889\\
6	1.58776504632019\\
7	1.58809335949322\\
8	1.5881928373826\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=2,
ytick={0, 1, 2},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.10693759886133\\
2	1.11152957304454\\
3	1.1153740214668\\
4	1.11770662066146\\
5	1.11834620668734\\
6	1.11879936603067\\
7	1.11890444505621\\
8	1.11953756000214\\
9	1.11961027059849\\
10	1.1199195311366\\
11	1.12011494881618\\
12	1.12017416958603\\
13	1.12033284686217\\
14	1.12033895948864\\
15	1.12040846172897\\
16	1.12041390652564\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.05608889731275\\
2	1.08431501210806\\
3	1.10834050856176\\
4	1.11891055117252\\
5	1.12321530567299\\
6	1.12470216682288\\
7	1.12523793678797\\
8	1.12552298915589\\
9	1.12642268676024\\
10	1.12689100352585\\
11	1.127202079253\\
12	1.12763006638833\\
13	1.12766695997673\\
14	1.12788476342969\\
15	1.1278991085713\\
16	1.12794901573584\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

>>>>

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,3.296in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=5,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213595499958\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

@@

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,2.586in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=3.16339693422903,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	3.16197544010622\\
2	3.16257985135002\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	3.16115798980538\\
2	3.16339693422903\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,1.877in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=2.24021589430493,
ytick={0, 2, 4},
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	2.23378952118842\\
2	2.23654464483002\\
3	2.23679993610816\\
4	2.23713622127432\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.22545319620151\\
2	2.23919103086275\\
3	2.23937811584463\\
4	2.24021589430493\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,1.168in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=2,
ytick={0, 1, 2},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.57492536161738\\
2	1.58019558798915\\
3	1.58142030797172\\
4	1.58199169722726\\
5	1.58244513043393\\
6	1.58255247448636\\
7	1.58277901011216\\
8	1.58278544606781\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.54658301793324\\
2	1.57890604600973\\
3	1.58567053153604\\
4	1.58602764687811\\
5	1.58742152113889\\
6	1.58776504632019\\
7	1.58809335949322\\
8	1.5881928373826\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.376in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=2,
ytick={0, 1, 2},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.10693759886133\\
2	1.11152957304454\\
3	1.1153740214668\\
4	1.11770662066146\\
5	1.11834620668734\\
6	1.11879936603067\\
7	1.11890444505621\\
8	1.11953756000214\\
9	1.11961027059849\\
10	1.1199195311366\\
11	1.12011494881618\\
12	1.12017416958603\\
13	1.12033284686217\\
14	1.12033895948864\\
15	1.12040846172897\\
16	1.12041390652564\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.05608889731275\\
2	1.08431501210806\\
3	1.10834050856176\\
4	1.11891055117252\\
5	1.12321530567299\\
6	1.12470216682288\\
7	1.12523793678797\\
8	1.12552298915589\\
9	1.12642268676024\\
10	1.12689100352585\\
11	1.127202079253\\
12	1.12763006638833\\
13	1.12766695997673\\
14	1.12788476342969\\
15	1.1278991085713\\
16	1.12794901573584\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

### 2021-08-12 assets/waveform_wpt_modulated.tex
:bento: Update assets

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,3.251in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=5,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213595034367\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

@@

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,2.553in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=5,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.000570870326956724\\
2	4.4721359179404\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.0110856763978608\\
2	4.47212221176042\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,1.855in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=5,
ytick={0, 2, 4},
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.82810775851695e-05\\
2	3.53085892593064e-05\\
3	3.54347120351704e-05\\
4	4.42555930751421\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.22676166428777e-05\\
2	2.19662118918467e-05\\
3	2.35611473414708e-05\\
4	4.38314990531919\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,1.157in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=1,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	6.25263040326118e-06\\
2	6.27921380470113e-06\\
3	6.34955721457943e-06\\
4	6.35150273149039e-06\\
5	6.42390701416729e-06\\
6	6.42457974220412e-06\\
7	6.47741859691329e-06\\
8	6.47969375628299e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.07597912435039e-05\\
2	2.10621157490525e-05\\
3	2.27177871268911e-05\\
4	2.34764127724776e-05\\
5	0.000633429285281999\\
6	0.00299168089473067\\
7	0.0168627108170759\\
8	0.0302609478988545\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=1,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.46841221768753e-06\\
2	1.46853581584948e-06\\
3	1.46888556831603e-06\\
4	1.46960879811052e-06\\
5	1.47063822579491e-06\\
6	1.47112726920342e-06\\
7	1.47158812622008e-06\\
8	1.47177039924161e-06\\
9	1.47273523214333e-06\\
10	1.47288042283048e-06\\
11	1.47389962773962e-06\\
12	1.47396082891411e-06\\
13	1.47467419234042e-06\\
14	1.47476166458671e-06\\
15	1.47506643379659e-06\\
16	1.47509099313304e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.08632407458004e-05\\
2	1.08877007745949e-05\\
3	1.09594364217047e-05\\
4	1.10938027865036e-05\\
5	1.12827891666553e-05\\
6	1.15378065652616e-05\\
7	1.19617266900702e-05\\
8	1.41613520483063e-05\\
9	6.92466622068608e-05\\
10	0.000224790946436711\\
11	0.000536194940235116\\
12	0.0020179447121528\\
13	0.00228142595005787\\
14	0.00484194141261625\\
15	0.00509975660438143\\
16	0.00611499201390601\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

>>>>

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,3.251in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
ymax=5,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={at={(0.5,1.03)}, anchor=south, legend columns=2, legend cell align=left, align=left, draw=white!15!black},
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	4.47213595034367\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{IRS: {\boldmath${s}$}$_{\mathrm{I}}$}

@@

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,2.553in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
ymax=5,
ytick={0, 2, 4},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.000570870326956724\\
2	4.4721359179404\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.0110856763978608\\
2	4.47212221176042\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,1.855in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ymax=5,
ytick={0, 2, 4},
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.82810775851695e-05\\
2	3.53085892593064e-05\\
3	3.54347120351704e-05\\
4	4.42555930751421\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.22676166428777e-05\\
2	2.19662118918467e-05\\
3	2.35611473414708e-05\\
4	4.38314990531919\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,1.157in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
ymax=1,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	6.25263040326118e-06\\
2	6.27921380470113e-06\\
3	6.34955721457943e-06\\
4	6.35150273149039e-06\\
5	6.42390701416729e-06\\
6	6.42457974220412e-06\\
7	6.47741859691329e-06\\
8	6.47969375628299e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	2.07597912435039e-05\\
2	2.10621157490525e-05\\
3	2.27177871268911e-05\\
4	2.34764127724776e-05\\
5	0.000633429285281999\\
6	0.00299168089473067\\
7	0.0168627108170759\\
8	0.0302609478988545\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.42in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ymax=1,
ytick={0, 1},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\large}, label style={font=\large}, ticklabel style={font=\large}, legend style={font=\large}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	1.46841221768753e-06\\
2	1.46853581584948e-06\\
3	1.46888556831603e-06\\
4	1.46960879811052e-06\\
5	1.47063822579491e-06\\
6	1.47112726920342e-06\\
7	1.47158812622008e-06\\
8	1.47177039924161e-06\\
9	1.47273523214333e-06\\
10	1.47288042283048e-06\\
11	1.47389962773962e-06\\
12	1.47396082891411e-06\\
13	1.47467419234042e-06\\
14	1.47476166458671e-06\\
15	1.47506643379659e-06\\
16	1.47509099313304e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	1.08632407458004e-05\\
2	1.08877007745949e-05\\
3	1.09594364217047e-05\\
4	1.10938027865036e-05\\
5	1.12827891666553e-05\\
6	1.15378065652616e-05\\
7	1.19617266900702e-05\\
8	1.41613520483063e-05\\
9	6.92466622068608e-05\\
10	0.000224790946436711\\
11	0.000536194940235116\\
12	0.0020179447121528\\
13	0.00228142595005787\\
14	0.00484194141261625\\
15	0.00509975660438143\\
16	0.00611499201390601\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%
